\begin{frame}
\frametitle{Agenda for the day}
\begin{itemize}
\item 9:00 Start
\item \textasciitilde{}10:15 Break, 20 minutes
\item \textasciitilde{}11:30 Break, 20 minutes
\item 12:30 Lunch break
\item 13:30 Start of afternoon session
\item \textasciitilde{}14:45 Break, 20 minutes
\item \textasciitilde{}16:00 Break, 20 minutes
\item 17:00 End
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Overall agenda - today}
\begin{itemize}
\item Intro
\item Kernel sources, branches and versions
\item Kernel configuration, building, booting
\item Kernel modules
\item Describing hardware, device tree, pin control
\item Driver model and frameworks
\item The i2c subsystem
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Overall agenda - 2nd day}
\begin{itemize}
\item Overflow from last time
\item The input subsystem
\item Memory management
\item Memory-mapped I/O
\item The misc subsystem
\item Scheduling, sleeping, interrupts, concurrency
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Overall agenda - 3d day}
\begin{itemize}
\item Overflow from last time
\item DMA
\item Debugging
\item Power management and related frameworks
\item Closing thoughts
\end{itemize}
\end{frame}

\begin{frame}

\frametitle{Participate!}
During the lectures...
\begin{itemize}
\item Don't hesitate to ask questions. Other people in the audience may have
similar questions too.
\item Don't hesitate to share your experience too, for example to compare Linux
with other operating systems you know.
\item Your point of view is most valuable, because it can be similar to your
colleagues' and different from the trainer's.
\item During practical sessions, ask help from your neighbours.
\item All this helps the trainer to engage with participants, see when
something needs clarifying and make the session more interactive, enjoyable
and useful for everyone.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Collaborate!}
  As in the Free Software and Open Source community,
  collaboration between participants is valuable in this training session:
  \begin{itemize}
    \item Use the dedicated Mattermost channel for this session
	  to add questions.
    \item You can also report issues, share screenshots and command output there.
    \item Don't hesitate to share your own answers and to help others
          especially when the trainer is unavailable.
    \item The Mattermost channel is also a good place to ask questions
	  outside of training hours, and after the course is over.
    \end{itemize}
\end{frame}
